Conditional selectivity for triplestores

### 2012-09-07 conditional/trunk/selectivity-basic.tex
fix label
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@366 43ef1190-90fd-4dd7-a769-d0121f02b80e
oooh, noooooes
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@367 43ef1190-90fd-4dd7-a769-d0121f02b80e

\begin{equation}\label{eq:selsubjun}
sel(T_{?~p~o}) = sel(O | P) \cdot sel(P) . 
\end{equation}

@@

\begin{equation}\label{eq:selsubjunp}
sel(P = p) = \frac{\rdfterm{void:propertyPartition/void:triples}}{|d|}
\end{equation}
and
\begin{equation}\label{eq:selsubjunop}
sel(O = o|P = p) =
\frac{\rdfterm{void:propertyPartition/void:distinctObjects}}{\rdfterm{void:propertyPartition/void:triples}} .
\end{equation}

Thus,
\begin{equation}\label{eq:selsubjunop}
sel(T_{?~p~o}) =
\frac{\rdfterm{void:propertyPartition/void:distinctObjects}}{|d|} .
\end{equation}\todo{wtf}

>>>>

\begin{equation}\label{eq:selsubjun}
sel(T_{\{?~p~o\}}) = sel(O | P) \cdot sel(P) . 
\end{equation}

@@

\begin{equation}\label{eq:selsubjunp}
sel(P = p) = \frac{\rdfterm{void:propertyPartition/void:triples}}{|d|}
\end{equation}
and
\begin{equation}\label{eq:selsubjunop}
sel(O = o|P = p) =
\frac{\rdfterm{void:propertyPartition/void:distinctObjects}}{\rdfterm{void:propertyPartition/void:triples}} .
\end{equation}
Thus,
\begin{equation}\label{eq:selsubjunres}
sel(T_{\{?~p~o\}}) =
\frac{\rdfterm{void:propertyPartition/void:distinctObjects}}{|d|} ,
\end{equation}\todo{WRONG!}
where the notation is inspired by SPARQL 1.1 Property Paths,
for example the relevant part of a VoID description for the second
example in section~\ref{sec:example} would be:
\begin{verbatim}
</dataset> a void:Dataset ;
           void:propertyPartition [
                void:property foaf:firstName;
                void:distinctObjects 2 .
           ]
\end{verbatim}

there exists a \rdfterm{void:propertyPartition} predicate that
has an object which is again linked to a dataset subset containing the
property $p$ as predicate of \text
